Flowchart of Current Algorithm

### 2009-02-03 docs/flowchart/flowchart.tex
clarified some of the future considerations

@@

\MarginPar{Instead of calling Correct Base, if we set $\rho_0 = \overline\rho$, 
we don't even need $\nabla\cdot\etarho\er$.}
\item {\bf Correct Base}$[\rho_0^{\inp}, (\nabla\cdot\etarho\er)^{\inp}] \rightarrow [\rho_0^{\outp}]$\\
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$.  For both plane-parallel and spherical
we use
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \dt (\nabla\cdot\etarho\er)^{\inp}_j \enskip . 
\end{equation}

\MarginPar{what about an $\eta_{\rho h}$?}
\end{enumerate}

>>>>

%-----------------------------------------------------------------------------
% Future Considerations
%-----------------------------------------------------------------------------

\section{Future Considerations}

\item Should we eeplace {\bf Correct Base} with $\rho_0 = {\rm{\bf Avg}}(\rho)$ in 
plane-parallel and $\rho_0 = \rho_0 - {\rm{\bf Avg}}(\rho_0 - \rho)$ in spherical?
This eliminates the need for $\nabla\cdot\etarho$.

\item In {\bf Step 4} and {\bf Step 8}, should we move {\bf Correct Base} so it 
occurs immediately before {\bf Advect Base Pressure}?  Since the full
enthalpy advance ``feels'' the effects of the time-centered $\etarho$, we should
rely on a $\rho_0^{n+1}$ that also feels the effects.

\item Should we use a predictor-corrector for updating the full-state density?
Specifically, after calling {\bf Correct Base}, should we do a full-state density 
advance and {\bf Correct Base} using the more accurate estimate of $\rho_0^{n+1}$?

\item After {\bf React State}, should we set $(\rho h)_0 = {\rm{\bf Avg}}(\rho h)$ in 
plane-parallel and $(\rho h)_0 = (\rho h)_0 - {\rm{\bf Avg}}[(\rho h)_0 - (\rho h)]$ 
in spherical?  This can currently be done by making {\tt full\_rhoh0\_evolution = FALSE}.
This means that {\bf React Base} no longer has to exist, and the intermediate states, 
$(\rho h)_0^{(1)}$ and $(\rho h)_0^{(2)}$, no longer have to exist.  
{\bf Advect Base Enthalpy} will advance $(\rho h)_0^n \rightarrow (\rho h)_0^{n+1}$ 
directly.  This also means we don't have to deal with $\eta_{\rho h}$ or a 
{\bf Diffuse Base}.

\item Should we eliminate {\bf Advect Base Pressure} entirely, and instead directly
enforce HSE after {\bf Correct Base}?  {\bf Advect Base Pressure} was just a fancy
way of enforcing HSE anyway, so why not just compute the new pressure directly?

@@

\item {\bf Correct Base}$[\rho_0^{\inp}, (\nabla\cdot\etarho\er)^{\inp}] \rightarrow [\rho_0^{\outp}]$\\
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$.  For both plane-parallel and spherical
we use
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \dt (\nabla\cdot\etarho\er)^{\inp}_j \enskip . 
\end{equation}
